### 2020-01-19 defesa/tex/chapter/mcer.tex
wip

@@

\begin{figure}
	\centering
	\caption{An optimal solution before and after applying \autoref{lema:mce_2b}.}
	\includegraphics{tex/figures/scripts/ellipse-2-points}
	\fautor
	\label{fig:ellipse-2-points}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\caption{A $(E, u, v)$-feasible angle and a not $(E, u, v)$-feasible angle.}
	\includegraphics[scale=.8]{tex/figures/scripts/feasible-angle}
	\fautor
	\label{fig:feasible-angle}
\end{figure}

@@

	With this result in hands, we can use a continuity argument to complete our proof as follows.
	Let $\delta : \Phi_j(u,v) \mapsto \R^2$ be a continuous function which takes an angle $\theta\in\Phi_j(u,v)$ and returns a center, such that $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$, and, from solution $(Q', \Theta')$, $\delta(\theta_j') = q_j'$.
	In general, for any angle in $\Phi_j(u,v)$, there are two possible centers that make $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$ (see \autoref{fig:2point-ellipse} for an example), however, as $\delta(\theta_j') = q_j'$, $\delta$ is well-defined.

@@

	We have that $f_w(q_j', \theta_j^*) < 1$ for all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)$. We then define function $g_w\colon \Phi_j(u,v) \mapsto \R_{\ge0}$ as $g_w(\theta) = f_w(\delta(\theta), \theta)$. As $g_w$ is a composition of continuous functions, it is also continuous.

	Therefore, for any $\theta\in\Phi_j(u,v)$, if a point $w \in \Pp \cap E_j(q_j^*, \theta_j^*)$ leaves the coverage of the ellipse, it must have $g_w(\theta)>1$, which by continuity, there must be another $\hat{\theta}$, such that $g_w(\hat{\theta})=1$, which means that $w\in \partial E_j(\delta(\hat{\theta}), \hat{\theta})$, contradicting the hypothesis. The same can be said about a point that enters the coverage of $E_j$.
\end{proof}

\begin{figure}[H]
	\centering
	\caption{Every ellipse that contains two points for a fixed angle of rotation.}
	\includegraphics[scale=.36]{tex/figures/2point-ellipse}
	\fautor
	\label{fig:2point-ellipse}
\end{figure}

>>>>

Next, a notation is defined for the set of equivalent solutions of an optimal solution which has at least two points on the border of every ellipse.

@@

\begin{figure}
	\centering
	\caption{An optimal solution before and after applying \autoref{lema:mce_2b}.}
	\includegraphics[scale=.38]{tex/figures/ellipse-2-points}
	\fautor
	\label{fig:ellipse-2-points}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\caption{A $(E, u, v)$-feasible angle and a not $(E, u, v)$-feasible angle.}
	\includegraphics[scale=.33]{tex/figures/feasible-angle2}
	\fautor
	\label{fig:feasible-angle}
\end{figure}

@@

	With this result in hands, we can use a continuity argument to complete our proof as follows.
	Let $\delta : \Phi_j(u,v) \mapsto \R^2$ be a continuous function which takes an angle $\theta\in\Phi_j(u,v)$ and returns a center, such that $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$, and, from solution $(Q', \Theta')$, $\delta(\theta_j') = q_j'$.
	In general, for any angle in $\Phi_j(u,v)$, there are two possible centers that make $\{u,v\} \subset \partial E_j(\delta(\theta), \theta)$ (see \autoref{fig:feasible-angle} for an example), however, as $\delta(\theta_j') = q_j'$, $\delta$ is well-defined.

@@

	For all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j^*) < 1$. We then define a function $g_w\colon \Phi_j(u,v) \mapsto \R_{\ge0}$ as $g_w(\theta) = f_w(\delta(\theta), \theta)$. As $g_w$ is a composition of continuous functions, it is also continuous.

	Therefore, for any $\theta\in\Phi_j(u,v)$, if a point $w \in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus\{u,v\}$ is not covered by $E_j(\delta(\theta), \theta)$, it must have $g_w(\theta)>1$. Then, by continuity, another angle $\hat{\theta} \in(\theta_j^*, \theta)$ must exist, such that $g_w(\hat{\theta})=1$, which means that $w\in \partial E_j(\delta(\hat{\theta}), \hat{\theta})$, contradicting the hypothesis. The same can be said about a point that enters the coverage of $E_j(\delta(\theta), \theta)$.
\end{proof}

%\begin{figure}[H]%
%	\centering%
%	\caption{Every ellipse that contains two points for a fixed angle of %rotation.}
%	\includegraphics[scale=.36]{tex/figures/2point-ellipse}
%	\fautor
%	\label{fig:2point-ellipse}
%\end{figure}
